---
title: 'Transit-Oriented Development'
author: "E Chin Li"
date: "09/19/2023"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    theme: readable
---
# Preparation

## Set Up

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = FALSE
)
# Load Libraries
library(tidyverse)
library(tidycensus)
library(sf)
library(kableExtra)
library(plotly)
library(tmap)

options(scipen=999)
options(tigris_class = "sf")

#Load qBr & q5 & theme & other source
source("https://raw.githubusercontent.com/urbanSpatial/Public-Policy-Analytics-Landing/master/functions.r")

# Load color palette
palette5 <- c("#f0f9e8","#bae4bc","#7bccc4","#43a2ca","#0868ac")

# Census API Key
census_api_key("ee5bb303d562a134a5fc2cdbc4ab53c8d0ca7629", overwrite = TRUE)
```

## Wrangling 2009 & 2017 ACS Data

```{r include=TRUE, results="hide", message=FALSE, warning=FALSE}
#2009data
tracts09 <-  
  get_acs(geography = "tract",
          variables = c("B02001_001E", #total population
                        "B19013_001E", #median HH income
                        "B25058_001E", #median rent
                        "B06012_002E", #total poverty
                        "B25001_001E", #HH units number
                        "B08301_001E", #total people commute
                        "B08301_012E"), #total people commute by subway
          year=2009, 
          state= "DC",
          geometry=TRUE,
          output="wide") %>% 
  st_transform('ESRI:102728') %>% 
  rename(
    TotalPop = B02001_001E,
    MedHHInc = B19013_001E, 
    MedRent = B25058_001E,
    TotalPoverty = B06012_002E,
    HHUnits = B25001_001E,
    TotalCommute = B08301_001E,
    SubwayCommute = B08301_012E
  ) %>% 
   mutate(pctRent = MedRent / MedHHInc *100,
         perHHUnitPop = TotalPop / HHUnits,
         pctPoverty = TotalPoverty / TotalPop*100,
         pctSubwayCommute = SubwayCommute / TotalCommute*100,
         year = "2009") %>%
    dplyr::select(-NAME, -TotalPoverty, -TotalCommute, -SubwayCommute, -starts_with("B"))

#2017data
tracts17 <-  
  get_acs(geography = "tract",
          variables = c("B02001_001E", #total population
                        "B19013_001E", #median HH income
                        "B25058_001E", #median rent
                        "B06012_002E", #total poverty
                        "B25001_001E", #HH units number
                        "B08301_001E", #total people commute
                        "B08301_012E"), #total people commute by subway
          year=2017, 
          state= "DC",
          geometry=TRUE,
          output="wide") %>% 
  st_transform('ESRI:102728') %>% 
  rename(
    TotalPop = B02001_001E,
    MedHHInc = B19013_001E, 
    MedRent = B25058_001E,
    TotalPoverty = B06012_002E,
    HHUnits = B25001_001E,
    TotalCommute = B08301_001E,
    SubwayCommute = B08301_012E
  ) %>% 
   mutate(pctRent = MedRent / MedHHInc *100,
         perHHUnitPop = TotalPop / HHUnits,
         pctPoverty = TotalPoverty / TotalPop*100,
         pctSubwayCommute = SubwayCommute / TotalCommute*100,
         year = "2017") %>%
    dplyr::select(-NAME, -TotalPoverty, -TotalCommute, -SubwayCommute, -starts_with("B"))

#combine 2009 & 2017
allTracts <- rbind(tracts09,tracts17)
```

## Wrangling Subway Data

```{r  include=TRUE, results="hide", message=FALSE, warning=FALSE}
#Wrangling Subway Data
metroStops <- st_read("https://raw.githubusercontent.com/EChinLee/MUSA508_Homework/HW2/Metro_Stations_in_DC.geojson")%>%
  st_transform(st_crs(tracts09))

  metroStops$line <- ifelse(metroStops$LINE=="red"|metroStops$LINE=="green"|metroStops$LINE=="orange",metroStops$LINE,"transfer station")

ggplot() + 
  geom_sf(data=st_union(tracts09)) +
  geom_sf(data=metroStops, 
          aes(colour = line), 
          show.legend = "point", size= 2) +
  scale_colour_manual(values = c("red" = "#8E2323", "green" = "#426F42", "orange" = "#E47833","transfer station" = "#4F2F4F")) +
  labs(title="Metro Stops", 
       subtitle="Washington DC", 
       caption="Fig 1 (Source: opendata.dc.gov)") +
  mapTheme()
```

## Create Buffer

```{r  include=TRUE}
#two kinds of buffer
stopBuffer <- st_buffer(metroStops, 2640)

stopUnion <- st_union(st_buffer(metroStops, 2640))

metroBuffers <- 
  rbind(
     stopBuffer %>%
      mutate(Legend = "Buffer") %>%
      dplyr::select(Legend),
     stopUnion %>%
      st_sf() %>%
      mutate(Legend = "Unioned Buffer"))

#visualization buffers
ggplot() +
  geom_sf(data = metroBuffers) +
  geom_sf(data = metroStops, show.legend = "point") +
  facet_wrap(~Legend) + 
  labs(caption = "Figure 2") +
  mapTheme()
```

## Use Buffers to Visualize Spatial Population Data

```{r  include=TRUE, warning=FALSE}
# union buffer as filter
buffer <- filter(metroBuffers, Legend=="Unioned Buffer")

#clip
clip <- 
  st_intersection(buffer, tracts09) %>%
  dplyr::select(TotalPop) %>%
  mutate(Selection_Type = "Clip")

#spatial selection
spatialselection <- 
  tracts09[buffer,] %>%
  dplyr::select(TotalPop) %>%
  mutate(Selection_Type = "Spatial Selection")

#select by centroids
selectCentroids <-
  st_centroid(tracts09)[buffer,] %>%
  st_drop_geometry() %>%
  left_join(., dplyr::select(tracts09, GEOID), by = "GEOID") %>%
  st_sf() %>%
  dplyr::select(TotalPop) %>%
  mutate(Selection_Type = "Select by Centroids")

#Plotting the results of each method
intersections <- rbind(clip, spatialselection, selectCentroids)

ggplot() +
  geom_sf(data=intersections, aes(fill = TotalPop)) +
  geom_sf(data=metroStops, show.legend = "point") +
  scale_fill_viridis_c() +
  facet_wrap(~Selection_Type) + 
  labs(caption = "Figure 3(Source: opendata.dc.gov)") +
  mapTheme()
```

## Brief Introduction

# TOD Indicators Analysis

## TOD Indicators Visualizations

```{r  include=TRUE, warning=FALSE}
#indicator of TOD / Non-TOD
allTracts.group <- 
  rbind(
    st_centroid(allTracts)[buffer,] %>%
      st_drop_geometry() %>%
      left_join(allTracts) %>%
      st_sf() %>%
      mutate(TOD = "TOD"),
    st_centroid(allTracts)[buffer, op = st_disjoint] %>%
      st_drop_geometry() %>%
      left_join(allTracts) %>%
      st_sf() %>%
      mutate(TOD = "Non-TOD")) %>%
  mutate(MedRent.inf = ifelse(year == "2009", MedRent * 1.14, MedRent)) 

#plot TOD change
ggplot() + 
  geom_sf(data = st_union(tracts09)) +
  geom_sf(data = allTracts.group,
          aes(fill = TOD)) +
  labs(title="2009 & 2017 TOD Distribution", 
       subtitle="Washington DC", 
       caption="Fig 4(Source: opendata.dc.gov)") +
  scale_fill_manual(values = c("TOD" = "#FEB35E", "Non-TOD" = "#81B2D4") ) +
  facet_wrap(~year)+
  #scale_colour_manual(values = c("TOD" = "#FEB35E", "Non-TOD" = "#81B2D4") ) +
  mapTheme()

#% of Income spent on Rent visualization
ggplot() + 
  geom_sf(data = st_union(tracts09)) +
  geom_sf(data = allTracts.group,
          aes(fill = q5(pctRent)
              ) )+
  geom_sf(data = buffer, fill = "transparent", color = "red") +
  labs(title="2009 & 2017 Percentage of Household Income Spent on Rent", 
       subtitle="Washington DC", 
       caption="Fig 5(Source: opendata.dc.gov)") +
  facet_wrap(~year)+
  scale_fill_manual(values = palette5 ) +
  mapTheme()

#People per Housing Unit visualization
ggplot() + 
  geom_sf(data = st_union(tracts09)) +
  geom_sf(data = allTracts.group,
          aes(fill = q5(perHHUnitPop)
              ) )+
  geom_sf(data = buffer, fill = "transparent", color = "red") +
  labs(title="2009 & 2017 People per Household Unit", 
       subtitle="Washington DC", 
       caption="Fig 6(Source: opendata.dc.gov)") +
  facet_wrap(~year)+
  scale_fill_manual(values = palette5 ) +
  mapTheme()

#poverty percentage visualization
ggplot() + 
  geom_sf(data = st_union(tracts09)) +
  geom_sf(data = allTracts.group,
          aes(fill = q5(pctPoverty)
              ) )+
  geom_sf(data = buffer, fill = "transparent", color = "red") +
  labs(title="2009 & 2017 Percentage of Poverty", 
       subtitle="Washington DC", 
       caption="Fig 7(Source: opendata.dc.gov)") +
  facet_wrap(~year)+
  scale_fill_manual(values = palette5 ) +
  mapTheme()

#% of subway commute in total visualization
ggplot() + 
  geom_sf(data = st_union(tracts09)) +
  geom_sf(data = allTracts.group,
          aes(fill = q5(pctSubwayCommute)) )+
  geom_sf(data = buffer, fill = "transparent", color = "red") +
  labs(title="2009 & 2017 Percentage of Subway in Total Commute Means", 
       subtitle="Washington DC", 
       caption="Fig 8(Source: opendata.dc.gov)") +
  facet_wrap(~year)+
  scale_fill_manual(values = palette5 ) +
  mapTheme()
```

## TOD Indicator Tables

```{r  include=TRUE, warning=FALSE}
# TOD Indicator Tables years & TOD
allTracts.Summary <- 
  st_drop_geometry(allTracts.group) %>%
  group_by(year, TOD) %>%
  summarize(Rent = mean(MedRent, na.rm = T),
            Population = mean(TotalPop, na.rm = T),
            Percent_Income_on_Rent = mean(pctRent, na.rm = T),
            People_per_Household_Unit = mean(perHHUnitPop, na.rm = T),
            Percent_Poverty = mean(pctPoverty, na.rm = T),
            Percent_Subway_in_Commute = mean(pctSubwayCommute, na.rm = T))

kable(allTracts.Summary) %>%
  kable_styling(full_width = F, bootstrap_options = c("striped", "hover", "condensed") )%>%
  footnote(general_title = "\n",
           general = "Table 1(Source: opendata.dc.gov)")

# TOD Indicator Tables Variables
allTracts.Summary %>%
  unite(year.TOD, year, TOD, sep = ": ", remove = T) %>%
  gather(Variable, Value, -year.TOD) %>%
  mutate(Value = round(Value, 2)) %>%
  spread(year.TOD, Value) %>%
  kable() %>%
  kable_styling(full_width = F, bootstrap_options = c("striped", "hover", "condensed")) %>%
  footnote(general_title = "\n",
           general = "Table 2(Source: opendata.dc.gov)")
```

## TOD Indicator Plots

```{r  include=TRUE, warning=FALSE}
# TOD Indicator four visualization Plots
allTracts.Summary %>%
  gather(Variable, Value, -year, -TOD) %>%
  ggplot(aes(year, Value, fill = TOD)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~Variable, scales = "free", ncol=5) +
  scale_fill_manual(values = c("#bae4bc", "#0868ac")) +
  labs(title = "Indicator differences across time and space",
       subtitle="Washington DC", 
       caption="Fig 9(Source: opendata.dc.gov)") +
  plotTheme() + theme(legend.position="bottom")
```

## Graduated Symbol Maps of Population and Rent within 0.5 mile of each Transit Station

```{r  include=TRUE, warning=FALSE}
# change geometry into x & y
metroStopscoord <- metroStops %>% 
                  st_transform(st_crs('ESRI:102728')) %>% 
                  dplyr::mutate(x = sf::st_coordinates(.)[,1], 
                                y = sf::st_coordinates(.)[,2]) %>%
                  distinct(NAME, .keep_all=TRUE) %>%
                  dplyr::select(-LINE, -line)

#add x & y to the orginal data forming new data
new_allTracts.group <- allTracts.group %>% st_join(metroStopscoord)

#graduated symbol maps of population
ggplot() +
  geom_sf(data = new_allTracts.group, alpha = 0.4) +
  geom_point(data = new_allTracts.group, aes(x = x, y = y, size = TotalPop, color = "red"), alpha = 0.5) +
  scale_size_area(max_size = 15) + #size change
  #scale_color_gradient(low = "blue", high = "red") +  # color change
  geom_sf(data = metroStops, size = 1, color = "black") + #station point
  labs(title = "Population within 0.5 mi. of Subway Stations", 
       subtitle = "Washington, DC", 
       caption = "Fig 10(Source: US Census Bureau; opendata.dc.gov)") +
  facet_wrap(~year) +
  mapTheme()

#graduated symbol maps of rent
ggplot() +
  geom_sf(data = new_allTracts.group, alpha = 0.4) +
  geom_point(data = new_allTracts.group, aes(x = x, y = y, size = MedRent, color = "red"), alpha = 0.5) +
  scale_size_area(max_size = 15) + #size change
  #scale_color_gradient(low = "blue", high = "red") +  # color change
  geom_sf(data = metroStops, size = 1, color = "black") + #station point
  labs(title = "Rent within 0.5 mi. of Subway Stations", 
       subtitle = "Washington, DC", 
       caption = "Fig 11(Source: US Census Bureau; opendata.dc.gov)") +
  facet_wrap(~year) +
  mapTheme()

#or show the population & rent in one graduated symbol
ggplot() +
  geom_sf(data = new_allTracts.group, alpha = 0.4) +
  geom_point(data = new_allTracts.group, aes(x = x, y = y, size = TotalPop, color = MedRent), alpha = 0.5) +
  scale_size_area(max_size = 15) + #size change
  scale_color_gradient(low = "blue", high = "red") +  # color change
  geom_sf(data = metroStops, size = 1, color = "black") + #station point
  labs(title = "Population and Rent within 0.5 mi. of Subway Stations", 
       subtitle = "Washington, DC", 
       caption = "Fig 12(Source: US Census Bureau; opendata.dc.gov)") +
  facet_wrap(~year) +
  mapTheme()
```

## Geomline Plot Shows Mean Rent as a Function of Distance to Transit Stations

```{r  include=TRUE, warning=FALSE}
allTracts <- rbind(tracts17,tracts09)
metro_MRB <- multipleRingBuffer(st_union(metroStops), 47520, 2640)

allTracts.rings <-
  st_join(st_centroid(dplyr::select(allTracts, GEOID, year)),
          metro_MRB) %>%
  st_drop_geometry() %>%
  left_join(dplyr::select(allTracts, GEOID, MedRent, year), 
            by=c("GEOID"="GEOID", "year"="year")) %>%
  st_sf() %>%
  mutate(distance = distance / 5280) #convert to miles

#multipleRingBuffer visualization
  ggplot() +
    geom_sf(data=metro_MRB) +
    geom_sf(data=metroStops, size=1) +
    geom_sf(data=st_union(tracts17), fill=NA, size=1.2) +
    labs(title="Half mile buffers",
         subtitle="Washington DC", 
       caption="Fig 13(Source: opendata.dc.gov)") +
    mapTheme()

 allTracts.rings.summary <- st_drop_geometry(allTracts.rings) %>%
    group_by(distance, year) %>%
    summarize(Mean_Rent = mean(MedRent, na.rm=TRUE))

#geom_line plot
ggplot(allTracts.rings.summary,
       aes(distance, Mean_Rent, colour=year)) +
      geom_point(size=3) + 
  geom_line(size=2) +
  labs(title="Mean Rent as a Function of Distance to Transit Station",
         subtitle="Washington DC", 
       caption="Fig 14(Source: US Census Bureau; opendata.dc.gov)") 
```

# Conclusion

## Household Preferences for Transit-Rich Neighborhoods

## Economic Shift Influenced by Population in TODs

## Spatial Biases and Margin of Error
